Predator clusters

### 2023-07-02 reports/04_pred_clus.qmd
Begin looking at sea ice 65% contour

```{r}
library(ggridges)

pred_clust_ice <- tibble(
  amlr.station = names(clust),
  pred_clust = factor(clust,
                      labels = c("Open", "Marginal", "Pagophilic"))
) %>% 
  left_join(station_ice,
            by = "amlr.station") %>% 
  drop_na(ice_coverage)

>>>>

```{r}
pred_clust_ice <- tibble(
  amlr.station = names(clust),
  pred_clust = factor(clust,
                      labels = c("Open", "Marginal", "Pagophilic"))
) %>% 
  left_join(station_ice,
            by = "amlr.station") %>% 
  drop_na(ice_coverage)
